Removing CO Interlopers from [\CII] Surveys With the Three Field Approach

### 2019-03-04 paper/ms.tex
Add macros, title material
Add preliminary abstract

\newcommand{\Msun}{\ensuremath{\text{M}_\odot}}
\newcommand{\pc}{\ensuremath{\text{pc}}}
\newcommand{\kpc}{\ensuremath{\text{kpc}}}
\newcommand{\Mpc}{\ensuremath{\text{Mpc}}}
\newcommand{\Myr}{\ensuremath{\text{Myr}}}
\newcommand{\Gyr}{\ensuremath{\text{Gyr}}}

\newcommand{\CII}{C~\textsc{ii}}

@@

@@

>>>>

\newcommand{\Msun}{\ensuremath{\text{M}_\odot}}
\newcommand{\pc}{\ensuremath{\text{pc}}}
\newcommand{\kpc}{\ensuremath{\text{kpc}}}
\newcommand{\Mpc}{\ensuremath{\text{Mpc}}}
\newcommand{\Myr}{\ensuremath{\text{Myr}}}
\newcommand{\Gyr}{\ensuremath{\text{Gyr}}}
\newcommand{\SFR}{\ensuremath{\text{SFR}}}

\newcommand{\CI}{C~\textsc{i}}
\newcommand{\CII}{C~\textsc{ii}}
\newcommand{\OIII}{O~\textsc{iii}}

@@

\newcommand{\penn}{Department of Physics \& Astronomy, University of
Pennsylvania, 209 South 33rd St., Philadelphia, PA 19104, USA}

@@

\title{Removing CO Interlopers from [\CII] Surveys With the Three Field
Approach}

\email{abeane@sas.upenn.edu}

\author{Angus Beane}
\affil{\penn}

\author{Adam Lidz}
\affil{\penn}

\author{others}

\begin{abstract}
Intensity mapping stands to be a promising probe of the large-scale structure
of the universe at high redshift ($z>3$). The experiment TIME, currently
undergoing a preliminary engineering run, will measure [\CII] emission from
the redshift ranges $5<z<9$ {\bf check}. An important problem to overcome will
be to remove interloping CO lines. These are lines that are emitted at a
different frequency than [\CII] but are observed at the same frequency from
gas residing at a different redshift. The measurement of [\CII] will be
impacted by emission from three CO transitions
\end{abstract}
